Scientific Reasoning with LLMs

### 2024-10-29 docs/proposal/main.tex
Matrikelnummer
Update main.tex

%we'll probably have a group number later
%names are given in alphabetical order
\author{Stuttgart Team: Florian Dreyer \and Ekaterina Kolos \and Daria Matyash}

@@

Scientific machine reasoning is ...

>>>>

%we'll probably have a group number later
%names are given in alphabetical order
\author{Stuttgart Team: Florian Dreyer (3667877) \and Ekaterina Kolos \and Daria Matiash (3668740)}

@@

Scientific machine reasoning is the application of AI techniques to simulate scientific reasoning processes, such as  data interpretation, hypothesis generation, and causal inference. It facilitates scientific inquiry and discovery by enabling machines to independently analyze scientific data, generate hypotheses, and make predictions.
